Linear Algebra as a Unifying Theory\\of Wireless Workload Modeling

### 2008-02-04 paper.tex
Work on common model expressions.

\newcommand{\X}{\mathsf{X}}
\newcommand{\M}{\mathsf{M}}
\newcommand{\E}[1]{\left<#1\right>}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Qt}{Q_{\text{time}}}
\newcommand{\Qi}{Q_{\text{ival}}}
\newcommand{\Di}{Q^{-1}_{\text{ival}}}
\newcommand{\ones}[1]{\mathbf{1}_{#1}}

@@

\subsection{Communication Topology}

@@

\subsection{Flow Packet Count, Size \& Duration}
\label{sec:flow-totals}

From the matrices $Z$ and $V$, we can compute the packet count, size (total bytes), and approximate duration for each flow. The computations for size and duration require knowing the values that each matrix column represents. The computed duration is only approximate because information is irrecoverably lost in the quantization process (see \Equation{interval-quantization}). The vectors of representative values for $Z$ and $V$ are:
\begin{align}
\vec{\sigma}&=(1,2,3,\dots,d_z),\\
\vec{\tau}&=\seq{\Di\left(k,\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
Using these vectors of representative values, the vector of packet-counts is $Z\ones{d_z}=V\ones{d_v}$, the vector of flow sizes vector is $Z\vec{\sigma}$, and the vector of durations is $V\vec{\tau}$.

@@

It is common in generating traffic behaviors for experiments to treat packets, nodes, and flows uniformly to varying degrees, largely because of the high complexity of doing otherwise and the lack of compelling alternatives. Here we examine how various notions of uniformity are represented in the matrix model. In general, \textit{intra-flow uniformity} is effected by right multiplication, which mixes the elements in each row, whereas \textit{inter-flow uniformity} is effected by left multiplication, which mixes elements across rows. The standard constant bit-rate (\caps{CBR}) flow model, for example, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals. Each flow's bit-rate is therefore constant, and hence the name. The strict \caps{CBR} model can be expressed simply using the packets-bytes-duration model discussed in \Section{representations}. Deriving the packet-bytes-duration model from the general matrix model is accomplished through right multiplication as described in \Section{flow-totals}.

>>>>

\newcommand{\X}{\mathsf{X}}
\newcommand{\M}{\mathsf{M}}
\newcommand{\E}[1]{\left<#1\right>}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Qt}{Q_{\text{time}}}
\newcommand{\Qi}{Q_{\text{ival}}}
\newcommand{\Di}{Q^{-1}_{\text{ival}}}
\newcommand{\ones}[1]{\mathbf{1}_{#1}}
\newcommand{\zeros}[1]{\mathbf{0}_{#1}}

@@

\subsection{Nodes: Communication Topology}
\label{sec:communication-topology}

@@

\subsection{Flows: Packet Count, Size \& Duration}
\label{sec:flow-totals}

From the matrices $Z$ and $V$, we can compute the packet count, size (total bytes), and approximate duration for each flow. The computations for size and duration require knowing the values that each matrix column represents. The computed duration is only approximate because information is irrecoverably lost in the quantization process (see \Equation{interval-quantization}). The vectors of representative values for $Z$ and $V$ are:
\begin{align}
\vec{\sigma}&=\seq{1,2,3,\dots,d_z},\\
\vec{\tau}&=\seq{\Di\left(k,\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
Using these representative values, the vector of packet-counts is $Z\ones{d_z}=V\ones{d_v}$, the vector of flow sizes vector is $Z\vec{\sigma}$, and the vector of approximate durations is $V\vec{\tau}$.

\subsection{Network: Marginal Behavior}
\label{sec:marginal-behavior}

\noindent
...

@@

It is common in generating traffic behaviors for experiments to treat packets, nodes, and flows uniformly to varying degrees, largely because of the high complexity of doing otherwise and the lack of compelling alternatives. Here we examine how various notions of uniformity are expressed in the matrix model. In general, \textit{intra-flow uniformity} is effected by right multiplication, which mixes the elements in each row, whereas \textit{inter-flow uniformity} is effected by left multiplication, which mixes elements across rows. The constant bit-rate (\caps{CBR}) flow model, for example, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals; thus each flow's bit-rate is constant, as the name implies. The strict \caps{CBR} model can be expressed simply using the packets-bytes-duration (\caps{PBD}) model used as an example in \Section{representations}. The pair of matrices $\seq{Z,V}$ is transformed to \caps{PBD} form using the vectors defined in \Section{flow-totals}: $\seq{Z,V}\Gamma$, where
\begin{align}
\Gamma=\begin{pmatrix}
\ones{} & \vec{\sigma} & \zeros{} \\
\zeros{} & \zeros{} & \vec{\tau}
\end{pmatrix} \in \R^{(d_v+d_z)\times{3}}.
\end{align}

%Deriving the packet-bytes-duration model from the general matrix model is accomplished through right multiplication as described in \Section{flow-totals}.
% TODO: this conclusion is pretty weak.
